\documentclass[12pt]{article}

\usepackage{sbc-template}

\usepackage{graphicx,url}

%\usepackage[brazil]{babel}   
\usepackage[utf8]{inputenc}  

     
\sloppy

\title{Travelling Salesperson Problem:\\ Different Approaches and Performance in Exponential Time}

\author{Juan M. Braga F.\inst{1}}


\address{Departamento de Ciência da Computação -- Universidade Federal de Minas Gerais
  (UFMG)\\
  Av. Pres. Antônio Carlos, 6627 -- Pampulha -- Belo Horizonte -- MG -- Brazil
  \email{juanbraga@ufmg.br}
}

\begin{document} 

\maketitle

\begin{abstract}
  This paper documents the practical aspects of implementing solutions
  for the Travelling Salesperson Problem, a well known difficult problem that requires
  exponential time for the optimal solution. Three algorithms were implemented:
  an exact solution through the branch-and-bound technique, and two other approximations,
  the twice-around-the-tree and Christofides algorithms.
\end{abstract}
     
\begin{resumo} 
  Este artigo documenta os aspectos práticos da implementação de soluções
  para o Problema do Caixeiro Viajante, um problema bem conhecido e difícil que requer
  tempo exponencial para encontrar a solução ótima. Foram implementados três algoritmos:
  uma solução exata através da técnica de branch-and-bound, e duas outras aproximações,
  os algoritmos twice-around-the-tree e Christofides.
\end{resumo}


\section{Introducing the Travelling Salesperson Problem}

The Travelling Salesperson Problem (TSP) is aptly described by [BRILLIANT] 

\begin{quote}
  "A salesperson needs to visit a set of cities to sell their goods. They know how 
  many cities they need to go to and the distances between each city. In what order 
  should the salesperson visit each city exactly once so that they minimize their 
  travel time and so that they end their journey in their city of origin?"
\end{quote}

The TSP is a well known \textbf{intractable problem}, which in the context of 
algorithms means that the time and/or space required to solve the problem grows 
exponentially with the size of the input, making it impractical to solve even for 
relatively small inputs.

This project documents the development of three solutions for the given problem, 
focusing on evaluating the real-world challenges associated with them, such as planning and 
optimization, making informed decisions on data structures and libraries, and 
analyzing the usage of computer resources.

\section{Modelling and Implementation} \label{sec:firstpage}
    Descreve as implementações utilizadas. Deve-se apresentar com detalhes a
    escolha da estimativa de custo; estruturas de dados usadas e o porquê; escolha
    de best-first ou depth-first no algoritmo de branch-and-bound; além de
    qualquer outro detalhe de implementação e dos algoritmos em si.

The TSP problem can be conveniently modeled by a weighted graph, with the graph's 
nodes representing the cities and the edge weights specifying the distances.

To solve it, three algorithms were implemented in this project: an optimal solution using 
the branch-and-bound technique, and two approximations, the twice-around-the-tree and the 
Christofides algorithms.

\subsection{Optimal Solution}

Branch and bound is a general method that tries to divide a problem into smaller subproblems,
and then makes informed decisions to discard some of these subproblems to reach the optimal solution.

To consider it in the TSP context, one benefits from picturing the problem as a tree, where each node 
represents a city and each edge a path between two cities. Then, the first node can be any city 
(since one can start from any city of the optimal path), and the branch and bound must make the decision 
of which city to visit next based on all o the previous decisions (cities visited).

The parameter for selecting the next city is calculated by summing the distance of the current path 
with the minimum distance to any unvisited city. By maintaining a lower bound on the distance of 
the optimal solution, the branch and bound algorithm discards subproblems that cannot possibly 
lead to the optimal solution, effectively focusing on promising paths.

\subsection{Approximate Solution: Twice Around the Tree}

[TODO DESCRIPTION OF TWICE-AROUND-THE-TREE]
[guarantee of 2 of optimal solution]

\subsection{Approximate Solution: Christofides}

[TODO DESCRIPTION OF CHRISTOFIDES]
[guarantee of 3/2 of optimal solution]

\section{Experiments} \label{sec:firstpage}

\subsection{Twice Around the Tree algorithm}

The results show that the algorithm is very fast, and consumes the least amount
of memory among all of the others. However, it is also the least accurate, with
    Apresentar os experimentos e discutir os resultados. Você deve avaliar os
    limites de cada algoritmo/implementação, tentando buscar uma relação entre
    tamanho da instância e desempenho. Deve também comparar os algoritmos
    entre si. Tente responder quando cada implementação se sai melhor ou
    deveria ser usada.

\section{}
    Apresente as conclusões do seu trabalho. Mostre o quê pôde ser percebido
    com seus experimentos.

\section{References}

https://brilliant.org/wiki/traveling-salesperson-problem/
https://www.cs.ubc.ca/~hutter/previous-earg/EmpAlgReadingGroup/TSP-JohMcg97.pdf
https://www.youtube.com/watch?v=GiDsjIBOVoA
http://comopt.ifi.uni-heidelberg.de/software/TSPLIB95/
https://www.overleaf.com/latex/templates/sbc-conferences-template/blbxwjwzdngr
https://www.youtube.com/watch?v=dNCwtFJLsKI&pp=ygUmY2hpc3RvZmlkZXMgYWxnb3JodG0gc2F1Y2VsZXNzZ2l1c2VwcGU%3D
https://networkx.github.io/documentation/latest/index.html

\bibliographystyle{sbc}
\bibliography{sbc-template}

\end{document}
